03 Data Vizualization

### 2022-11-28 03_data_viz.Rmd
new figure draft

# Summarized turnover

turnover_summarized <- readRDS("cache/turnover_summarized.RDS")

@@

# IRMS chromatogram data
sample_files <- readRDS(file = "cache/sample_files.RDS")
```

@@

@@

p_lit_turnover_w_ours <- lit_turnover_w_ours %>%
  filter(method_type != "Microscopy") %>% 
  # order by mean turnover rate
  ggplot(
    aes(x = -n,
        y = u_d_mn,
        fill = method_type,
        label = round(gen_d, 1)
        )
    ) +
  geom_col() +
  geom_text(nudge_y = 0.05, size = 2) +
  coord_flip(ylim = c(0, 0.5)) +
  scale_fill_manual(values = literature_values_swatch_2) +
  labs(y = TeX("Turnover (d$^{-1}$)"),
       fill = "Method") +
  theme_classic() +
  theme(axis.title.y = element_blank(),
        axis.text.x = element_text(angle = 0, hjust = 0.5, size = 14),
        axis.ticks.y = element_blank(),
        axis.text.y = element_blank(),
        axis.title.x = element_text(size = 18),
        #legend.position = "bottom",
        plot.title = element_text(hjust = 0.5),
        legend.position = c(0.85, 0.1),
        legend.text = element_text(size = 15),
        legend.title = element_blank(),
        plot.margin = margin(1,1,1.5,1.2, "in"))
p_lit_turnover_w_ours

@@

@@

>>>>

# Summarized turnover
turnover_summarized <- readRDS("cache/turnover_summarized.RDS")

@@

# IRMS chromatogram data
sample_files <- readRDS(file = "cache/sample_files.RDS")

# IRMS Error Estimation
sF_0 <- readRDS(file = "cache/sF_0.RDS")

@@

### Draft 2

```{r}
p_dF2 <- turnover_summarized %>% 
  filter(
    compound %nin% c("H2", "20:0", "22:0", "24:0", "a-15:0")) %>% 
  ungroup() %>% 
  select(terrain, inc_time_d, compound, dF_mc, calibrated_at2H_with_memory_correction_se) %>%
  left_join(
    turnover_weighted %>% 
      select(terrain, inc_time_d, dF_weighted_mc), 
    by = c("terrain", "inc_time_d")) %>% 
  group_by(
    terrain,
    inc_time_d
  ) %>% 
  pivot_longer(
    cols = c(dF_mc, dF_weighted_mc),
    values_to = "dF", 
    names_to = "type"
  ) %>% 
  mutate(compound = case_when(
    type == "dF_weighted_mc" ~ "Weighted Mean",
    TRUE ~ compound
  )) %>%
  mutate(
    terrain = case_when(
      terrain == "Gordon Gulch Conifer Forest" ~ "Conifer Forest",
      terrain == "Marshall Mesa Grassland" ~ "Grassland",
      terrain == "Niwot Ridge Tundra" ~ "Tunrda"
  )) %>%

  ggplot(
    aes(
      x = inc_time_d,
      y = dF * 10000, # convert from at% to ppm
      group = compound,
      color = terrain,
      fill = terrain,
      alpha = type,
      size = type
    )
  ) +
  geom_borderline(
    color = "gray",
    alpha = 1,
    size = 0.5
    ) +
  geom_point() +
  facet_wrap(vars(terrain)) +
  scale_color_manual(values = terrain_color_swatch) +
  scale_fill_manual(values = terrain_fill_swatch) +
  scale_alpha_discrete(range = c(0.2, 1)) +
  scale_size_discrete(range = c(1.5, 2)) +
  scale_x_continuous(breaks = c(0, 1,2,3,4,5,6,7)) +
  theme_classic() +
  labs(
    x = "Time elapsed (days)",
    y = TeX("$ \\Delta ^2H$ (ppm)")
  ) +
  theme(legend.position = "none",
        strip.background = element_blank(),
        plot.title = element_text(hjust = 0.5),
        axis.title.x = element_text(size = 10),
        panel.grid.major.y = element_line(linetype = "dotted"))
p_dF2

@@

p_lit_turnover_w_ours <- lit_turnover_w_ours %>%
  filter(method_type != "Microscopy") %>% 
  # order by mean turnover rate
  ggplot(
    aes(x = -n,
        y = u_d_mn,
        fill = method_type,
        label = round(gen_d, 1)
        )
    ) +
  geom_col() +
  #geom_text(nudge_y = 0.05, size = 2) +
  coord_flip(ylim = c(0, 0.5)) +
  scale_fill_manual(values = literature_values_swatch_2) +
  labs(y = TeX("Turnover (d$^{-1}$)"),
       fill = "Method") +
  theme_classic() +
  theme(axis.title.y = element_blank(),
        axis.text.x = element_text(angle = 0, hjust = 0.5, size = 14),
        axis.ticks.y = element_blank(),
        axis.text.y = element_blank(),
        axis.title.x = element_text(size = 18),
        #legend.position = "bottom",
        plot.title = element_text(hjust = 0.5),
        legend.position = c(0.85, 0.1),
        legend.text = element_text(size = 15),
        legend.title = element_blank(),
        plot.margin = margin(1,1,1.5,1.2, "in"))
p_lit_turnover_w_ours

@@

### Draft 2

# Colorblind friendly palette:
lit_values_swatch_3 <- c(
  "#20968d", # gray green
  "#6269EB", # blue
  "#E0187B", # pink
  "#26AFE1" # light blue 
  )
p_lit_turnover_w_ours2 <- lit_turnover_w_ours %>%
  filter(method_type != "Microscopy") %>% 
  ggplot(
  aes(
    x = -n,
    y = u_d_mn,
    fill = method_type,
    label = round(gen_d, 1)
    )
    ) +
  geom_col() +
  scale_fill_manual(
    values = lit_values_swatch_3
  ) +
  # scale_fill_viridis_d(
  #   begin = 0,
  #   end = 0.8
  # ) +
  coord_flip(ylim = c(0, 0.5)) +
  labs(
    y = TeX("Turnover (d$^{-1}$)"),
    fill = "Method"
  ) +
  theme_classic() +
  theme(
    axis.title.y = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    axis.line.y = element_blank(),
    legend.position = c(0.85, 0.8),
    legend.background = element_rect(color = "black"),
    legend.text = element_text(size = 15),
    legend.title = element_blank(),
  )
p_lit_turnover_w_ours2
# 
# cowplot::save_plot(filename = "fig_output/literature_values_draft2.pdf",
#                    plot = p_lit_turnover_w_ours2,
#                    base_height = 8,
#                    base_width = 10)

### Draft 2 Inset

```{r}
 p_lit_turnover_w_ours_inset <- lit_turnover_w_ours %>%
  filter(method_type != "Microscopy") %>%
  ggplot(
    aes(
      x = u_d_mn, 
      y = method_type,
      color = method_type
      )
  ) +
  geom_boxplot(width = 0.2) +
  coord_cartesian(xlim = c(0, 0.5)) +
  #ggdist::stat_pointinterval() +
  scale_color_manual(
    values = lit_values_swatch_3
  ) +
  labs(
    x = "",
    y = "",
    fill = "Method"
  ) +
  theme_classic() +
  theme(
    legend.position = "NA"
  )
p_lit_turnover_w_ours_inset
```

### Draw with inset

```{r}
p_literature2_w_inset <- ggdraw(p_lit_turnover_w_ours2) +
  draw_plot(
    p_lit_turnover_w_ours_inset, 
    x = 0.63, 
    y = 0.23, 
    width = 0.35, 
    height = 0.35
    )
p_literature2_w_inset
```

@@

## SF: IRMS Error Assessment

```{r}
# Pull the IRMS standard error for this experiment from the error of measuring standards
IRMS_standard_error <- sF_0 %>% select(F_0_at2H_se) %>% pull()
paste0("The standard error of IRMS is +/- ", IRMS_standard_error, "% (", IRMS_standard_error*10000, " ppm)")

test_standard_error_u <- tibble(
  a = 1,
  FT = IRMS_standard_error, # standard error in atom%
  F0 = 0.00000000000000000001, # start at zero
  t = seq(1, 100, by = 1), # time ranging between 0 and 100 days
  FL = 100, # label strength in atom%
  u = calculate_turnover(
    a = a,
    FT = FT,
    F0 = F0,
    t = t,
    FL = FL
  )
)

test_standard_error_u %>% 
  ggplot(
    aes(
      x = t,
      y = u
    )
  ) +
    geom_line() +
  labs(
    x = "Incubation Time",
    y = "Growth rate (day-1)",
    caption = paste0("Growth estimate resulting from", round(IRMS_standard_error*10000,4), " ppm F2H error across incubation times" )
  )
```

```{r}
error_testing <- turnover %>% 
  select(inc_time_d, dF, f_label, a, u_d_mc) %>% 
  mutate(F0 = 0) %>% 
  filter(
    inc_time_d != 0,
    !is.na(dF)) %>% 
  mutate(FT_se = IRMS_standard_error) %>% 
  mutate(
    u_d_FT_se = calculate_turnover(
      a = a, 
      FT = FT_se,
      F0 = F0,
      FL = f_label,
      t = inc_time_d
      ),
    turnover_ratio = u_d_FT_se / u_d_mc
  )

error_testing %>% 
  ggplot(
    aes(
      x = u_d_FT_se,
      fill = as.factor(inc_time_d),
      #shape = as.factor(f_label)
      )
  ) +
  geom_histogram() +
  labs(
    shape = "Label Strength (at%)",
    fill = "Incubation Time (Days)"
  )

error_testing_summary <- error_testing %>% 
  group_by(inc_time_d, f_label) %>% 
  summarize(
    u_d_FT_se_mn = mean(u_d_FT_se, na.rm = TRUE),
    FT_se_mn = mean(FT_se, na.rm = TRUE)
    ) %>% 
  rename(
    sensitivity_FT = FT_se_mn,
    sensitivity_u_d = u_d_FT_se_mn
    ) %>% 
  mutate(
    sensitivity_u_hr = sensitivity_u_d * 24,
    sensitivity_u_min = sensitivity_u_hr * 60,
    sensitivity_u_sec = sensitivity_u_min * 60
  ) %>% 
  select(inc_time_d, f_label, sensitivity_FT, sensitivity_u_d, sensitivity_u_hr, sensitivity_u_min, sensitivity_u_sec)

The resolution of LH-SIP is defined as the standard error of the IRMS instrument ($F_{SE}$) propagated through the turnover time calculation:

$$
\mu = - \frac{1}{t}ln(\frac{F_{SE} - a \cdot F_L}{F_0 - a \cdot F_L})
$$

Plugging in our standard error of:
```{r}
paste0("The standard error of IRMS is +/- ", IRMS_standard_error, "% (", IRMS_standard_error*10000, " ppm)")
```

```{r}
knitr::kable(error_testing_summary)
```
